A finite-state morphological transducer for Kyrgyz

### 2012-05-22 paper/paper.tex
paper fixes (!) and some poster work

The analyser is designed to be used with the longest-match left-to-right (LRLM) tokenisation strategy, as described in \cite{garrido-alenda02}. Thus when more than one `word' needs to be output, they are joined with the \texttt{+} symbol, which is reserved for joining two `words' in one analysis.  For example, [өнүктүрөбүзбү ?] \eng{will we develop it?} is analysed as 
өнүк{\tt {\small <v><tv><caus><aor><p1><pl>+}}бы{\tt {\small <qst>}}, which is two words: [өнүк] (verb, transitive, causative, aorist, first person, plural) and [бы] (question clitic).  Likewise, [келатсаң] \eng{if you come} кел{\tt {\small <v><iv><prt\_impf>}}+жат\texttt{{\small <vaux><gna\_cnd><p2><sg>}} is analysed as two words: [кел] (verb, intransitive, imperfect participle), and [жат] (auxiliary, conditional verbal adverb, second person, singular).

@@

The low vowel \{A\} also takes the backness and rounding of the preceding vowel, with the exception of when it occurs after /у/---n this case, it has an unrounded variant, as depicted in table~\ref{vowelharmonyA}.

>>>>

The analyser is designed to be used with the longest-match left-to-right (LRLM) tokenisation strategy, as described in \cite{garrido-alenda02}. Thus when more than one `word' needs to be output, they are joined with the \texttt{+} symbol, which is reserved for joining two `words' in one analysis.  For example, [өнүктүрөбүзбү ?] \eng{will we develop it?} is analysed as 
өнүк{\tt {\small <v><tv><caus><aor><p1><pl>+}}бы{\tt {\small <qst>}}, which is two words: [өнүктүрөбүз] (verb, transitive, causative, aorist, first person, plural) and [бы] (question clitic).  Likewise, [келатсаң] \eng{if you come} кел{\tt {\small <v><iv><prt\_impf>}}+жат\texttt{{\small <vaux><gna\_cnd><p2><sg>}} is analysed as two words: [кел] (verb, intransitive, imperfect participle), and [жат] (auxiliary, conditional verbal adverb, second person, singular).

@@

The low vowel \{A\} also takes the backness and rounding of the preceding vowel, with the exception of when it occurs after /у/---in this case, it has an unrounded variant, as depicted in table~\ref{vowelharmonyA}.
